Domain-specific working memory loads selectively increase negative interpertations of surprised facial expressions

### 2019-08-07 Manuscript/Manuscript.Rmd
change file save location

# Results
## Subjective ratings
```{r import data and analyze ratings, include = FALSE, echo = TRUE}
data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-08-01_12-38-57.csv")
### remove psych disorders ### Ask maital?
# data <- data[-c(4, 33, 37, 38, 41, 47),]

>>>>

# Results
## Subjective ratings
```{r import data and analyze ratings, include = FALSE, echo = TRUE}
data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-08-07_15-04-27.csv")
### remove psych disorders ### Ask maital?
# data <- data[-c(4, 33, 37, 38, 41, 47),]

### 2019-08-07 Manuscript/Manuscript.tex
change file save location

\begin{verbatim}
##              Df Sum Sq Mean Sq F value Pr(>F)  
## load          1  0.257 0.25709   4.599 0.0332 *
## type          1  0.002 0.00230   0.041 0.8394  
## load:type     1  0.001 0.00061   0.011 0.9170  
## Residuals   196 10.956 0.05590                 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\includegraphics{Manuscript_files/figure-latex/MAD-1.pdf}

>>>>

\includegraphics{Manuscript_files/figure-latex/MAD plot-1.pdf}
Finally, we assessed differences in maximum absolute deviation (MAD) across the WM trial conditions.
